Rare-event sampling applied to the simulation of extreme mechanical efforts exerted by a turbulent flow on a bluff body

### 2019-08-27 draft_p2.tex
Modifies legend caption for figure 6
Modifies comment and figure AMS_drag_resampling

\begin{figure}
	\centering
	\includegraphics[width=.6\linewidth]{return_time/return_time.png}
	\caption{Amplitude of drag fluctuation (in standard-deviation unit) as a function the corresponding return time.
	}
	\label{fig:return_time_instant}
\end{figure}

@@

% application
%
The \ac{ams} algorithm is applied to $N=256$ trajectories of duration $T_a = 20\tau_c$.
%
Fig.~\ref{fig:AMS_drag_resampling} displays the maximum drag achieved by the re-sampled trajectories as a function of the computational cost, similarly to Fig.~\ref{fig:comparaison_temps_de_retour}.
%
%
The distribution of the maximal drag for the \textit{initial} trajectories is also shown.
After a few iterations, the trajectories with the lowest maxima of the score function are discarded and new trajectories with higher maxima are re-sampled.
These maxima are depicted by the stars in Fig~\ref{fig:AMS_drag_resampling}.
Importantly, one can observe that the re-sampled trajectories never exceed the amplitude of the highest maximum already attained in the initial set of trajectories. This obviously contrasts with the case of the \acl{ou} process.
%(see Fig.~\ref{fig:comparaison_temps_de_retour}).

>>>>

\begin{figure}
	\centering
	\includegraphics[width=.6\linewidth]{return_time/return_time.png}
	\caption{Amplitude of drag fluctuations as a function the corresponding return time. $\tilde{f}_d$ denotes the drag with zero mean, \textit{i.e.} $\tilde{f}_d = f_d - \overline{f_d}$.
	}
	\label{fig:return_time_instant}
\end{figure}

@@

% application
%
The \ac{ams} algorithm is applied to $N=256$ trajectories of duration $T_a = 20\tau_c$.
%
Fig.~\ref{fig:AMS_drag_resampling} displays the maximum drag achieved by the re-sampled trajectories as a function of the computational cost, similarly to Fig.~\ref{fig:comparaison_temps_de_retour}.
%
%
The distribution of the maximal drag for the \textit{initial} trajectories is also shown.
After a few iterations, the trajectories with the lowest maxima of the score function are discarded and new trajectories with higher maxima are re-sampled.
Figure~\ref{fig:AMS_drag_resampling} shows the evolution of the maxima of the re-sampled trajectories as the \ac{ams} is iterated, \textit{i.e.} as a function of the computational cost.
The re-sampled trajectories never exceed the amplitude of the highest maximum already attained in the initial set of trajectories.
Note that the red points in figure~\ref{fig:AMS_drag_resampling} are analogous to the red line in  figure~\ref{fig:comparaison_temps_de_retour} for the \ac{ou} process.
%(see Fig.~\ref{fig:comparaison_temps_de_retour}).
